Dark matter halo shapes at $z=0$ in the Auriga simulations

### 2019-08-03 Document/paper.tex
edit

@@

Following the convergence criterion by \cite{VeraCiro11} in DM only simulations
we restrict the measurement of the ellipsoidal parameters to radii
between $2$ kpc and $R_{200}$ where  $R_{200}$ corresponds to the radius
computed enclosing a sphere with 200 times the critical density of the
Universe. 
This scale is similar to the gravitational smoothing length for
stellar particles. 
For this reason, in order to make the DM halo shape results comparable
against stellar disc shape measurements, we report our DM halo shape
results above $10$ kpc.
We characterize the stellar disk by measuring the angular momentum vector using the $10\%$ oldest stellar particles.

In our results we express the radius as a fraction of $R_{200}$ in
order to have a self-consistent dimensionless radius scale across all
halos. 
Given the small variance across halos, each dimensionless radius is associated with
a physical value with a mean value and a standard deviation.
For instance, over the 30 halos in the sample, the dimensionless
radius $R_{200}$ corresponds to a physical distance of $230\pm 16$
kpc.

@@

\begin{figure*}
\includegraphics[width=0.9\textwidth]{shape_resolution.pdf}
\caption{A}
\label{fig:resolution}
\end{figure*}

>>>>

\begin{figure*}
\includegraphics[width=0.9\textwidth]{shape_resolution.pdf}
\caption{Axial ratios for the six halos simulated at two different
  resolutions with two different physics (DMO and MHD). 
  In DMO simulations there is a good agreement between the two
  resolutions (L3 and L4) at all radii down to scales of $\approx 1$
  kpc from the center. 
  In MHD simulations there are noticeable differences at scales below
  $\approx 10$ kpc. 
  In this paper we only report results at scales larger $\approx 16$ kpc
  ($R_{200}/16$).}
\label{fig:resolution}
\end{figure*}

@@

Following the convergence criterion by \cite{VeraCiro11} in DM only simulations
we restrict the measurement of the ellipsoidal parameters to radii
between $1$ kpc and $R_{200}$ where  $R_{200}$ corresponds to the radius
computed enclosing a sphere with 200 times the critical density of the
Universe. 
{\bf However, this scale is similar to the gravitational smoothing length
for stellar particles.
For this reason we use the Level3 simulations performed at higher
resolution to gauge the convergence of the shape measurements in the
MHD simulations.

Figure \ref{fig:resolution} shows the results for the six halos
available at the higher Level3 resolution and the corresponding
halos at our baseline Level4 resolution. 
The dotted lines compare the DMO simulations showing that down to
scales of $1$ kpc the two simulations give comparable results.
In MHD simulations the situation is different, as expected. 
With the exception of Au-27 the shape ratios $b/a$ and $c/a$ start
to distantiate from each other for radii smaller than $15$ kpc.
Above these radii, the differences between the triaxility values at
Level4 and Level3 in MHD simulations are small and never exceed $0.1$.}

For this reason, in order to make the DM halo shape results comparable
against stellar disc shape measurements, we report all our shape
results above $10$ kpc.

In our results we express the radius as a fraction of $R_{200}$ in
order to have a self-consistent dimensionless radius scale across all
halos. 
Given the small variance across halos, each dimensionless radius is
associated with a physical value with a mean value and a standard deviation.
For instance, over the 30 halos in the sample, the dimensionless
radius $R_{200}$ corresponds to a physical distance of $230\pm 16$
kpc.  
Finally, we also measure the alignment of the halo shape against the
stellar disc angular momentum. 
We measure the angular momentum vector using the $10\%$ oldest stellar
particles within the virial radius.

@@
